Networked Character Devices

### 2011-12-10 report/presentation.tex
Added refrences for related work
Added refrences
Added copies of system overview diagrams and set toc depth to 1
Fixed minro types

\documentclass[handout]{beamer}
\usetheme{AnnArbor}
\usecolortheme{beaver}
\setbeamercovered{transparent=25}
\setbeamertemplate{blocks}[rounded][shadow=false]
\setbeamertemplate{navigation symbols}{}

@@

@@

\begin{frame}{Related Work}
  \begin{itemize}
    \item NFS
    \begin{itemize}
      \item Access to remote file system, but no devices
      \item Safe access
      \item http://nfs.sourceforge.net/
    \end{itemize}
    \item NBD
    \begin{itemize}
      \item Network Block Device- Introduced in Linux kernel 2.1.101
      \item Works with any file system but no exclusive access 
      \item http://nbd.sourceforge.net/
    \end{itemize}
    \item CUSE
    \begin{itemize}
      \item Character Device in User Space (extension of FUSE)- Linux kernel 2.6.31
      \item Used for OSS proxy for remote sound systems
      \item http://lwn.net/Articles/308445/
    \end{itemize}
    \item USB/IP Project
    \begin{itemize}
      \item USB device sharing over IP
      \item http://usbip.sourceforge.net/
    \end{itemize}

  \end{itemize}
\end{frame}

@@

\begin{frame}[t,fragile]{\texttt{udev}}
  \begin{lstlisting}[gobble=4,title=no way to set permissions within kernel,language=]
    ACTION=="add", SUBSYSTEM=="netchar", MODE="0666"
  \end{lstlisting}
  \begin{lstlisting}[gobble=4,title=cannot retroactively apply input attributes,language=]
    $ udevadm info -qall -n /dev/input/event8
    P: /devices/virtual/input/input8/event8
    N: input/event8
    E: DEVNAME=/dev/input/event8
    E: DEVPATH=/devices/virtual/input/input8/event8
    E: ID_INPUT=1
    E: ID_INPUT_KEY=1
    E: SUBSYSTEM=input
  \end{lstlisting}
\end{frame}

@@

\section{Results and Evaluation}
%---Full State Slide---%

\begin{frame}[c]{Full System}
  \begin{center}
    \includegraphics[height=0.75\paperheight,keepaspectratio]{system-full.png}
  \end{center}
\end{frame}

@@

  \begin{itemize}
  \item<1-> Supports exporting a single character device from the server
  \item<2-> Supports importing a single character device on the client
  \item<3-> Supports open, close, read, and write calls
  \item<4-> Supports basic Linux udev operation for automatic node
    creation on client
  \item<5-> Tested with various ``real'' and device files
  \end{itemize}

@@

\begin{itemize}
\item<1-> Does not work well when Character Device is not the exclusive
  device interface
  \begin{itemize}
  \item Many modern day devices interface directly with other
    in-kernel function, interfaces, and APIs
  \item procfs and sysfs provide additional device interface points
  \item Socket interfaces (netlink, etc) provide alternative to file
    system interfaces
  \end{itemize}
\item<2-> Requires exported devices to be ``de-integrated'' from host system
\item<3-> Requires QOS guarantees and high guilty network connection
\end{itemize}

@@

\begin{itemize}
\item<1-> A simple means to add network functionality to devices using
  well understood file semantics and interfaces.
\item<2-> The groundwork for cloud-like device pools and arrays
\item<3-> The means to efficiently export devices from where they are not
  need and import them where they can be used.
\end{itemize}

>>>>

\documentclass[handout]{beamer}
\usetheme{AnnArbor}
\usecolortheme{beaver}
\setbeamercovered{transparent=25}
\setbeamertemplate{blocks}[rounded][shadow=false]
\setbeamertemplate{navigation symbols}{}
\setcounter{tocdepth}{1}

@@

%---Full State Slide---%
\begin{frame}[c]{Full System}
  \begin{center}
    \includegraphics[height=0.75\paperheight,keepaspectratio]{system-full.png}
  \end{center}
\end{frame}

@@

\begin{frame}{Related Work}
  \begin{itemize}
  \item NFS \cite{nfs-source}
    \begin{itemize}
    \item Access to remote file system, but no devices
    \item Safe access
    \end{itemize}
  \item NBD \cite{nbd-source}
    \begin{itemize}
    \item Network Block Device- Introduced in Linux kernel 2.1.101
    \item Works with any file system but no exclusive access 
    \end{itemize}
  \item CUSE \cite{cuse-article}
    \begin{itemize}
    \item Character Device in User Space (extension of FUSE)
    \item Used for OSS proxy for remote sound systems
    \end{itemize}
  \item USB/IP Project \cite{usbip-source}
    \begin{itemize}
    \item USB device sharing over IP
    \end{itemize}
  \item Plan 9 \cite{plan9-pike}
    \begin{itemize}
    \item Full networked file based OS
    \item Allows sharing devices over a network via file interfaces
    \item Not widely deployed
    \end{itemize}
  \end{itemize}

@@

\begin{frame}[t,fragile]{\texttt{udev}}
  \begin{lstlisting}[gobble=4,title=no way to set permissions within kernel,language=]
    ACTION=="add", SUBSYSTEM=="netchar", MODE="0666"
  \end{lstlisting}
  \begin{lstlisting}[gobble=4,title=cannot retroactively apply input attributes,language=]
    $ udevadm info -qall -n /dev/input/event8
    P: /devices/virtual/input/input8/event8
    N: input/event8
    E: DEVNAME=/dev/input/event8
    E: DEVPATH=/devices/virtual/input/input8/event8
    E: ID_INPUT=1
    E: ID_INPUT_KEY=1
    E: SUBSYSTEM=input
  \end{lstlisting}
%$
\end{frame}

@@

\section{Results and Evaluation}
%---Full State Slide---%
\begin{frame}[c]{Full System}
  \begin{center}
    \includegraphics[height=0.75\paperheight,keepaspectratio]{system-full.png}
  \end{center}
\end{frame}

@@

  \begin{itemize}
  \item<1-> Supports exporting a single character device from the server
  \item<2-> Supports importing a single character device on the client
  \item<3-> Supports open, close, read, and write calls
  \item<4-> Supports basic Linux udev operation for automatic node
    creation on client
  \item<5-> Tested with various standard files and device files
  \end{itemize}

@@

\begin{itemize}
\item<1-> Does not work well when Character Device is not the exclusive
  device interface
  \begin{itemize}
  \item Many modern day devices interface directly with other
    in-kernel function, interfaces, and APIs
  \item procfs and sysfs provide additional device interface points
  \item Socket interfaces (netlink, etc) provide alternative to file
    system interfaces
  \end{itemize}
\item<2-> Requires exported devices to be ``de-integrated'' from host system
\item<3-> Requires QOS guarantees and high quality network connection
\end{itemize}

@@

\begin{itemize}
\item<1-> A simple means to add network functionality to devices using
  well understood file semantics and interfaces.
\item<2-> The groundwork for cloud-like device pools and arrays
\item<3-> The means to efficiently export devices from where they are not
  needed and import them where they can be used.
\end{itemize}
